---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```

# hsstools

<!-- badges: start -->
<!-- badges: end -->

The HSS Tools package is intended to automate and simplify the Human Security Survey's data cleaning and analysis process. 

## Installation

You can install the hsstools package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RenRMT/hsstools")
```

## Usage
The hsstools package automates a number of time-consuming steps in the data cleaning and analysis process.

### Cleaning
* `hss_surveyduration()` quickly calculates survey durations
* `hss_translate()` and `hss_mergetranslated()` add AR-EN translated text columns.

### Analysis
* `hss_table_single()` and `hss_table_multi()` generate contingency tables for the corresponding question types.
* `hss_format()` and `hss_label()` apply formatting and labelling of questions and response options based on information provided in the XLS form (in either English or Arabic).
* `hss_write_*()` and `hss_export_()` functions provide automation to create and export contingency tables based on a list questions taken from the XLS form.
  * `hss_write_tables()` and `hss_export_tables()` create an .xlsx file with tables and chi2 test outcomes.
  * `hss_write_formatted()` and `hss_export_formatted()` create a .docx (or .html) file with tables, chi2           outcomes, and appropriate formatting and labelling of questions and response options.
  
For an introduction to functions related to creating and exporting contingency tables see vignette("generating-tables"). For an introduction to functions related to data cleaning and wrangling see vignette("data-cleaning")

The hsstools package relies on a number of other packages. These package dependencies will be downloaded and installed automatically with the hsstools package. Additional packages installed are:

```{r, echo = FALSE}
writeLines(packageDescription("hsstools", fields = "Imports"))
```


